An example cleaning script

### 2025-03-18 code/processing-code/processingfile-v1.qmd
Part 3

```{r}
lmono6 <- lmono5 %>%
  mutate(food = case_when(
    `Isolation type` %in% c("environmental/other", "Not Sliced-Pork", "Sliced-Pork", 
                            "Not Sliced-Turkey", "Sausage Products-Pork", 
                            "Salad/Spread/Pate-Pork", "Salad/Spread/Pate-Chicken", 
                            "Meat/Nonmeat Combination-Beef", "Meat/Nonmeat Combination", 
                            "Sliced-Beef", "Sliced-Turkey", "Not Sliced-Chicken", 
                            "Meat/Nonmeat Combination-Other Poultry", 
                            "Meat/Nonmeat Combination-Combination species", "raw", 
                            "Meat/Nonmeat Combination-Chicken", 
                            "Sausage Products-Unknown species", 
                            "Meat/Nonmeat Combination-Turkey", 
                            "Sausage Products-Beef") & 
    !`Isolation source` %in% c("environmental swab", "environmental swab sponge floor", 
                               "condensate tray", "squeegee", "chain", "wrench", 
                               "underhopper", "environmental swab sponge non food contact surface", 
                               "environmental swab sponge pallet in cooler", 
                               "environmental swab of shelf", 
                               "Environmental Isolate, sponge swab") ~ "Yes",
    TRUE ~ "No"
  ))

```
#Finally, I want to remove the observations that are stool samples that will be bovine, pigeon and catbird
```{r}
lmono_final <- lmono6 %>%
  filter(!`Isolation type` %in% c("bos taurus", "pigeon", "catbird"))
```

>>>>

```{r}
lmono6 <- lmono5 %>%
  mutate(food = case_when(
    `Isolation type` %in% c("environmental/other", "Not Sliced-Pork", "Sliced-Pork", 
                            "Not Sliced-Turkey", "Sausage Products-Pork", 
                            "Salad/Spread/Pate-Pork", "Salad/Spread/Pate-Chicken", 
                            "Meat/Nonmeat Combination-Beef", "Meat/Nonmeat Combination", 
                            "Sliced-Beef", "Sliced-Turkey", "Not Sliced-Chicken", 
                            "Meat/Nonmeat Combination-Other Poultry", 
                            "Meat/Nonmeat Combination-Combination species", "raw", 
                            "Meat/Nonmeat Combination-Chicken", 
                            "Sausage Products-Unknown species", 
                            "Meat/Nonmeat Combination-Turkey", 
                            "Sausage Products-Beef") & 
    !`Isolation source` %in% c("environmental swab", "environmental swab sponge floor", 
                               "condensate tray", "squeegee", "chain", "wrench", 
                               "underhopper", "environmental swab sponge non food contact surface", 
                               "environmental swab sponge pallet in cooler", 
                               "environmental swab of shelf", 
                               "Environmental Isolate, sponge swab","environmental swab sponge") ~ "Yes",
    TRUE ~ "No"
  ))

```
#Finally, I want to remove the observations that are stool samples that will be bovine, pigeon and catbird
```{r}
lmono_final <- lmono6 %>%
  filter(!`Isolation type` %in% c("Bos taurus\"\"", "pigeon", "catbird"))
```
